Two-component thermal dust emission model: application to the {\it PLANCK} HFI maps

### 2014-05-14 ms.tex
revisions to relative zero level discussion

In the course of this study we use not only \PLANCK~857 GHz, but also all of
the remaining \PLANCK~HFI bands, as well as \verb|i100|. To derive the 
absolute zero level offsets that must be applied to each of the five
lowest-frequency \PLANCK~bands, we perform a regression versus the 
\PLANCK~857 GHz map corrected for the absolute zero level offset derived in
 $\S$\ref{sec:zp_abs}. We assume no offset need be applied
to \verb|i100|, which has a zero level tied to H\,\textsc{i} by SFD.

The need for additional low-order corrections beyond a simple scalar offset 
became evident upon inspecting the HFI maps at 100-545 GHz. In particular, we 
noticed the presence of a residual dipole pattern, with an orientation 
consistent with that of the Solar dipole. To most precisely recover the 
amplitude of the residual dipole, it is necessary to have the highest available
S/N in the independent variable of our regression. For this reason we have used
857 GHz as a reference for the 100-545 GHz bands, as opposed to the FDS99 
predictions or H\,\textsc{i}.

>>>>

In the course of this study we use not only \PLANCK~857 GHz, but also all of
the remaining \PLANCK~HFI bands, as well as \verb|i100|. To derive the 
zero level offsets that must be applied to each of the five lowest-frequency 
\PLANCK~bands, we perform a regression versus the \PLANCK~857 GHz map corrected
for the absolute zero level offset derived in $\S$\ref{sec:zp_abs}. We assume 
no offset need be applied to \verb|i100|, which already has its zero level 
tied to H\,\textsc{i}.

The need for additional low-order corrections beyond simple scalar offsets 
became evident upon inspecting the HFI maps at 100-545 GHz. In particular, we 
noticed the presence of a low-level dipole pattern, with an orientation 
consistent with that of the Solar dipole. Our strategy will be to 
simultaneously fit the residual dipole and zero-level offset amplitudes. To 
most precisely recover these amplitudes, it is necessary to have the highest 
available S/N in the independent variable of our regression. For this reason we
have used 857 GHz as a reference for the 100-545 GHz bands, as opposed to the 
FDS99 predictions or H\,\textsc{i} data.
